%\chapter{Corporate Social Responsibility}
\section{CSR Efforts}
The term "corporate social responsibility" (CSR) describes a company's efforts and deeds that go beyond its main business operations to benefit society, the environment, and its stakeholders. Like many big businesses, Schneider Electric has taken part in a number of CSR projects. The following are some broad areas where Schneider Electric has shown CSR efforts:

\begin{enumerate}
\item \textbf{Sustainability and Environmental Initiatives:} In order to lessen its carbon impact and advance environmental sustainability, Schneider Electric has made a commitment. This includes actions taken in its own operations as well as through its solutions and products to increase energy efficiency, lower greenhouse gas emissions, and encourage the use of renewable energy sources.

\item \textbf{Access to Energy: }Schneider Electric has started programs to give underprivileged people, particularly those in developing areas, access to dependable and sustainable electricity. This is in line with the Sustainable Development Goal (SDG) of the United Nations to ensure that everyone has access to modern, cheap, dependable, and sustainable energy.

\item\textbf{Ethical Business Practices:} CSR also includes moral business conduct including fostering openness, honesty, and ethical company governance. In the nations where it conducts business, Schneider Electric has probably made efforts to guarantee adherence to legal and regulatory requirements.

\item\textbf{Diversity and Inclusion:} Companies frequently make efforts to encourage diversity and inclusion among their employees and in their communities. This may entail initiatives to empower minority groups, advance gender equality, and develop equitable opportunity.

\item\textbf{Community Engagement:} Various community involvement and social development initiatives have been undertaken by Schneider Electric. Supporting regional projects for healthcare, education, and other community-based efforts might fall under this category.

\item\textbf{Circular Economy and Waste Reduction:} Schneider Electric's CSR activities also include programs to promote a circular economy and lessen waste. This can entail making products durable and recyclable.

\item\textbf{Partnerships and Collaboration:} To increase the effect of many CSR activities, partnership with philanthropic groups, governmental organizations, and other stakeholders is used.

\end{enumerate}

\section{Contribution to SDG}
In support of various Sustainable Development Goals (SDGs) set forth by the United Nations, Schneider Electric has been actively involved. The following implications of our initiative on the achievement of these SDGs are listed: 


\begin{enumerate}

\item\textbf{SDG 7- Affordable and Clean Energy:} The company's products and services help improve energy efficiency, promote the use of renewable energy sources, and provide access to reliable and sustainable energy, contributing to SDG 7's goal of ensuring affordable and clean energy for all. Our IoT based data acquisition system can assist in optimizing energy consumption, improving energy efficiency, and integrating renewable energy sources.

\item\textbf{SDG 9 - Industry, Innovation, and Infrastructure:} Schneider Electric's technologies and solutions play a significant role in advancing industrial automation, digital transformation, and infrastructure development. Their focus on innovation helps drive efficiency and sustainability across industries, contributing to SDG 9. A well-implemented DAS can enhance industrial processes, improve manufacturing efficiency, and facilitate innovation by providing real-time data insights. This can lead to more sustainable and efficient production methods, contributing to SDG 9's focus on building resilient infrastructure and promoting sustainable industrialization.

\item\textbf{SDG 11 - Sustainable Cities and Communities:} Schneider Electric's smart city solutions contribute to creating more sustainable and resilient urban environments. These solutions include smart grid technologies, energy-efficient building systems, and integrated urban infrastructure management. Our implemented data acquisition system can be employed to gather data related to urban infrastructure, and load management. Because of having remote maintenance feature in our project, zero carbon emission goals is being achieved, which is contributing to the goals of SDG 11


\item\textbf{SDG 12 - Responsible Consumption and Production: }Schneider Electric promotes responsible consumption and production through its efforts to improve energy efficiency, reduce waste, and support the transition to a circular economy. Their commitment to eco-design and product lifecycle management aligns with this goal. Data acquired through a DAS can help monitor resource consumption, waste generation, and production efficiency. By optimizing processes and reducing waste, companies can contribute to more responsible consumption and production patterns, orienting with SDG 12.

\item\textbf{SDG 13 - Climate Action:} The company's focus on energy efficiency, renewable energy, and reducing carbon emissions directly contributes to SDG 13's objective of combating climate change and its impacts. DAS can play a crucial role in monitoring environmental parameters such as air quality, noise, temperature, and emissions. Accurate and timely data collection can support climate change mitigation and adaptation efforts, helping to achieve the objectives outlined in SDG 13.

\end{enumerate}

\vspace{0.5cm}

Finally, Schneider Electric's Corporate Social Responsibility (CSR) initiatives stand out as evidence of the business' steadfast commitment to making the world a better place. They have successfully incorporated sustainability into their fundamental business processes through a thorough and forward-thinking strategy, going beyond simple compliance and embracing a greater purpose. Schneider Electric's dedication to social advancement, environmental protection, and moral behavior highlights their responsibility as a corporate citizen. Schneider Electric exemplifies how a global leader can generate good change while promoting innovation and cooperation by supporting programs that span from energy efficiency and renewable solutions to community empowerment and ethical governance.Schneider Electric continues to innovate and set an example for businesses throughout the world, demonstrating that social responsibility and commercial success are not incompatible but rather go hand in hand as we move toward a more sustainable and inclusive future.







\nomenclature{$CSR$}{Corporate Social Responsibility}
\nomenclature{$SDG$}{Sustainable Development Goals}